Tactic Script Optimisation for Aesop

### 2024-09-09 paper.tex
Minor changes to reordering section

    \Function{apply-step}{$\mathit{steps}, Φ, G, g, s$}
      \State \Let step $s$ be $(Φ^{\pre}, g, t, Φ^{\post}, G^{\post})$
      \State Run $t$ on $g$ in metavariable context $Φ$, producing context $Ψ$ and goals $G'$
      \If{goals $G'$ in context $Ψ$ are equal to $G^{\post}$ in $Φ^{\post}$}
        \State \Let $f$ be the partial map associating metavariables in $Φ^{\post}$ with matching metavariables in $Ψ$
        \State For each step in $\mathit{steps}$, replace its pre-goal $g^{\pre}$ with $f(g^{\pre})$ if $f(g^{\pre})$ is defined
        \State $s' \gets (Φ, g, t, Ψ, G')$
        \State \Let $G$ be $[g₁, \dots gₙ, g, k₁, \dots, kₘ]$
        \State \Let $G'$ be $[h₁, \dots, hₗ]$
        \State $H \gets [g₁, \dots, gₙ, h₁, \dots, hₗ, k₁, \dots, kₘ]$
        \State Remove from $H$ each goal that is assigned in $Ψ$
        \State $(\mathit{script}, Ω) \gets \Call{reorder-dynamic}{\mathit{steps}, Ψ, H}$
        \State \Return $(s' ∷ \mathit{script}, Ω)$
      \Else
        \State \Failure
      \EndIf
    \EndFunction
  \end{algorithmic}
  \caption{Dynamic reordering}\label{alg:dynamic-reordering}
\end{algorithm}

@@

If the goals are equal, the equality algorithm yields a partial bijective map $f$ that associates metavariables in $Φ^{\post}$ with their corresponding metavariables in $Ψ$.
We use this map to update the steps, replacing each pre-goal $g^{\pre}$ with its corresponding goal $f(g^{\pre})$ if $f(g^{\pre})$ is defined.
Without this update, when we later look up the step for, say, a goal $g$ produced by the current step, we would not find anything because the step's pre-goal is a goal that is equal to $g$, but it is not $g$ itself.

@@

Note that the step we prepend to the script is not the original step.
Rather, it is the step $\step{Φ}{g}{t}{Ψ}{G'}$ which retains the pre-goal $g$ and tactic $t$, but contains the pre-context $Φ$, the post-context $Ψ$ and the post-goals $G'$.
This is necessary because the old step's pre-context, post-context and post-goals are only $≡_{a}$-equal to $Φ$, $Ψ$ and $G'$; but when we later build a structured script from the reordered steps, each step's tactic must produce precisely its post-state.
Due to this update of the step, \textsc{reorder-dynamic} does not, in fact, merely reorder the steps but rather builds a new sequence of steps (with the same tactics).

>>>>

    \Function{apply-step}{$\mathit{steps}, Φ, G, g, s$}
      \State \Let step $s$ be $(Φ^{\pre}, g, t, Φ^{\post}, G^{\post})$
      \State Run $t$ in tactic state $(Φ, [g])$, producing tactic state $(Ψ, G')$
      \If{$(Φ^{\post}, G^{\post}) \aeq (Ψ, G')$}
        \State \Let $σ$ be the partial map from metavariables in $Φ^{\post}$ to matching metavariables in $Ψ$
        \State For each step in $\mathit{steps}$, replace its pre-goal $g^{\pre}$ with $σ(g^{\pre})$ if $g^{\pre} ∈ \dom(σ)$
        \State $s' \gets (Φ, g, t, Ψ, G')$
        \State \Let $G$ be $[g₁, \dots gₙ, g, k₁, \dots, kₘ]$
        \State \Let $G'$ be $[h₁, \dots, hₗ]$
        \State $H \gets [g₁, \dots, gₙ, h₁, \dots, hₗ, k₁, \dots, kₘ]$
        \State Remove from $H$ each goal that is assigned in $Ψ$
        \State $(\mathit{script}, Ω) \gets \Call{reorder-dynamic}{\mathit{steps}, Ψ, H}$
        \State \Return $(s' ∷ \mathit{script}, Ω)$
      \Else
        \State \Failure
      \EndIf
    \EndFunction
  \end{algorithmic}
  \caption{Dynamic reordering}\label{alg:dynamic-reordering}
\end{algorithm}

@@

If the goals are equal, the equality check yields a partial bijective map $σ$ that associates metavariables in $Φ^{\post}$ with their corresponding metavariables in $Ψ$.
We use this map to update the steps, replacing each pre-goal $g^{\pre}$ with its corresponding goal $σ(g^{\pre})$ if $σ(g^{\pre})$ is defined.
Without this update, when we later look up the step for, say, a goal $g$ produced by the current step, we would not find anything because the step's pre-goal is a goal that is equal to $g$, but it is not $g$ itself.

@@

Note that the step we prepend to the script is not the original step.
Rather, it is the step $\step{Φ}{g}{t}{Ψ}{G'}$ which retains the pre-goal $g$ and tactic $t$, but contains the pre-context $Φ$, the post-context $Ψ$ and the post-goals $G'$.
This is necessary because the old step's pre-context, post-context and post-goals are only $\aeq$-equal to $Φ$, $Ψ$ and $G'$; but when we later build a structured script from the reordered steps, each step's tactic must produce precisely its post-state.
Due to this update of the step, \textsc{reorder-dynamic} does not, in fact, merely reorder the steps but rather builds a new sequence of steps (with the same tactics).
